---
title: "asdf"
author: "RN7"
date: "January 12, 2018"
output: 
  md_document:
    variant: markdown_github
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages steel static}
library(dplyr)    # pipes and dplyr verbs
library(readr)    # reading in .csv files

library(ggplot2)  # plotting
library(ggthemes) # ggplot2 themes
library(scales)   # ggplot2 scaling options


Japan_Steel <- readxl::read_xls("Data/iron_steel_production_1948-2004.xls",
                             skip = 7,
                             col_names = c("J_Year", "Year", "Pig_iron", 
                                           "Ferro-alloys", "Crude_steel",
                                           "Hot_steel_products", "Galvanized_sheets")) %>% 
  select(Year, Crude_steel) %>% 
  filter(Year <= 1960)

Japan_Steel %>% 
  ggplot(aes(x = Year, y = Crude_steel)) + 
  geom_line(size = 2.5, color = "#474747") +
  scale_x_continuous(breaks = pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = pretty_breaks(), labels = comma, limits = c(0, 26000)) +
  geom_vline(xintercept = 1950) +
  geom_vline(xintercept = 1953) +
  annotate(geom = "text",
           label = "Korean\nWar", size = 5, color = "#474747",
           x = 1951.55, y = 17500) +
  theme_economist_white() +
  theme(axis.text = element_text(size = 10, color = "#474747"), 
        axis.title = element_text(size = 15, color = "#474747"),
        plot.title = element_text(hjust = 0.5, color = "#474747")) +
  labs(x = "Year", y = "Steel Production (Thousands of tons)", 
       title = "Japan Steel Production\n(1950-1960)",
       caption = "Source: Historical Statistics of Japan, 2012") 

```

## Introducing `gganimate`!

The idea behind gganimate is simple, as the name implies the animation part of a plot becomes just another aesthetic within the `ggplot` concept. This package is dependent on [ImageMagick](https://www.imagemagick.org/script/download.php) and FFmpeg to save your plots as GIFs or videos so make sure you have those installed as well. Once all that's done, go into the `ggplot()` code you previously made and it's just as simple as adding in `frame = ____ ` (whatever the variable you want to create an individual frame out of). You can also include `cumulative = TRUE` if you want to keep previous frames of added data on the plot as you change to the next frames. 

For other tutorials take a look at gganimate's [Github repo](https://github.com/dgrtwo/gganimate) for a short tutorial or take a look at Peter Aldhous' lecture notes on [Iteration & Animation (with ggplot2)](http://paldhous.github.io/ucb/2016/dataviz/week14.html).

If you're more of a video person or just want something to watch while grabbing some lunch here is David Robinson talking about gganimate at [Plotcon 2016](https://www.youtube.com/watch?v=9Y7Y1s4-VdA&t=1549s).

```{r steel animated, fig.show = "animate"}
library(gganimate) # animations

Steel_Animate <- Japan_Steel %>% 
  ggplot(aes(x = Year, y = Crude_steel, frame = Year, cumulative = TRUE)) + 
  geom_line(size = 2.5, color = "#474747") +
  scale_x_continuous(breaks = pretty_breaks(n = 10)) +
  scale_y_continuous(breaks = pretty_breaks(), labels = comma, limits = c(0, 26000)) +
  geom_vline(xintercept = 1950) +
  geom_vline(xintercept = 1953) +
  annotate(geom = "text",
           label = "Korean\nWar", size = 5, color = "#474747",
           x = 1951.55, y = 17500) +
  theme_economist_white() +
  theme(axis.text = element_text(size = 10, color = "#474747"), 
        axis.title = element_text(size = 15, color = "#474747"),
        plot.title = element_text(hjust = 0.5, color = "#474747")) +
  labs(x = "Year", y = "Steel Production (Thousands of tons)", 
       title = "Japan Steel Production\n(1950-1960)",
       caption = "Source: Historical Statistics of Japan, 2012") 

gganimate(Steel_Animate)

```
